\documentclass[twocolumn]{article}
\usepackage{graphics}
\usepackage{dcolumn}
\usepackage{multirow}
\newcolumntype{d}{D{.}{.}{2}}

\begin{document}
\tableofcontents
\section{Foo}


\begin{table}[ht]
\caption{table}
\centering
\begin{tabular}{|c|r|r|r|r|r|r|}
\hline
\multirow{2}*{ROUGE} &
\multicolumn{3}{c|}{spearman} \\ \cline{2-4}
    & case & segment & segment stop  \\ \hline
ROUGE-1 & 0.72 & 0.72 & 0.69 \\ \hline
ROUGE-2 & 0.72 & 0.72 & 0.69  \\ \hline
ROUGE-3 & 0.72 & 0.72 & 0.69 \\ \hline

\end{tabular}
\label{table:nonlin}
\end{table}

\begin{table}[ht]
\caption{table}
\centering
\begin{tabular}{|c|r|r|r|r|r|r|}
\hline
\multirow{2}*{ROUGE} &
\multicolumn{3}{c|}{spearman} &\multicolumn{3}{c|}{pearsonman} \\ \cline{2-7}
    & case & segment & segment stop & case & segment & segment stop \\ \hline
ROUGE-1 & 0.72 & 0.72 & 0.69 & 0.75 & 0.80 & 0.55 \\ \hline
ROUGE-2 & 0.72 & 0.72 & 0.69 & 0.75 & 0.80 & 0.55 \\ \hline
ROUGE-3 & 0.72 & 0.72 & 0.69 & 0.75 & 0.80 & 0.55 \\ \hline

\end{tabular}
\label{table:nonlin}
\end{table}


\begin{tabular}{|c|r|r|}

\hline
\multirow{2}*{name} &
\multicolumn{2}{c|}{score} \\ \cline{2-3}
    & language & math \\ \hline
zhangsan & 87 & 100 \\ \hline

\end{tabular}


\begin{tabular}{|c|r|r|}
\hline
& \multicolumn{2}{c|}{score} \\ \cline{2-3}
name & language & math \\ \hline
zhangsan & 87 &100 \\ \hline
\end{tabular}


\begin{tabular}{|r|r|}
\hline
\multicolumn{2}{|c|}{score} \\ \hline
language & math \\ \hline
87 & 100 \\ \hline
\end{tabular}


\begin{tabular}{|c|*{3}{d|}}
\hline
name & \multicolumn{1}{c|}{zhangsan} & \multicolumn{1}{c|}{lisi}
& \multicolumn{1}{c|}{wangwu} \\ \hline
income & 12345.6 & 5000 & 1020.55 \\ \hline
pay    & 765.43 & 5120.5 & 98760  \\ \hline
save   & 11580.17 & -120.5 & -97765.358 \\ \hline

\end{tabular}

\begin{tabular}{|c|rrr|p{4em}|}
\hline
   name & language & math & English & remark \\
\hline
   zhangsan & 87 & 100 & 93 & best \\
   lisi     & 75 & 63 & \emph{52} & makeup \\
   wangxiaoer & 80 & 82 & 78 & \\
\hline
\end{tabular}
\subsection{blah}
\begin{tabular}{|r|r|}
\hline
   output & input \\ \hline
   $-2$ & 4 \\
   0.01 & 	1.254 \\
   2    & 458.47 \\
\hline
\end{tabular}
\section{Bar}

\begin{tabular}{lcr}
left & center &right \\
column left & column center 
& column right\\
\end{tabular}

\begin{thebibliography}{8} % 这里的2是指参考文献总数目，需要根据实际情况进行修改
    \bibitem{bib1} Lin, Chin-Yew, and Eduard Hovy. "Automatic evaluation of summaries using n-gram co-occurrence statistics." Proceedings of the 2003 Conference of the North American Chapter of the Association for Computational Linguistics on Human Language Technology-Volume 1. Association for Computational Linguistics, 2003.
    \bibitem{bib2} Lin, Chin-Yew. "Rouge: A package for automatic evaluation of summaries." Text Summarization Branches Out: Proceedings of the ACL-04 Workshop. 2004.
	\bibitem{bib3}Lin, Chin-Yew, and Eduard Hovy. "Manual and automatic evaluation of summaries." Proceedings of the ACL-02 Workshop on Automatic Summarization-Volume 4. Association for Computational Linguistics, 2002.
	\bibitem{bib4}Nenkova, Ani, Rebecca Passonneau, and Kathleen McKeown. "The pyramid method: Incorporating human content selection variation in summarization evaluation." ACM Transactions on Speech and Language Processing (TSLP) 4.2 (2007): 4.
	\bibitem{bib5}Lin, Chin-Yew. "Looking for a few good metrics: Automatic summarization evaluation-how many samples are enough." Proceedings of the NTCIR Workshop. Vol. 4. 2004.
	\bibitem{bib6}Radev, Dragomir R., et al. "Evaluation challenges in large-scale document summarization." Proceedings of the 41st Annual Meeting on Association for Computational Linguistics-Volume 1. Association for Computational Linguistics, 2003.
	\bibitem{bib7}Radev, Dragomir R., Daniel Tam, and Günes Erkan. "Single-document and multi-document summary evaluation using Relative Utility."
	\bibitem{bib8}Donaway, Robert L., Kevin W. Drummey, and Laura A. Mather. "A comparison of rankings produced by summarization evaluation measures." Proceedings of the 2000 NAACL-ANLPWorkshop on Automatic summarization-Volume 4. Association for Computational Linguistics, 2000.
\end{thebibliography}
\end{document}